Multi-level modeling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-31 6-modelpresentation.tex
synchro
replace FML by \FML

\texttt{Process} represents an enacted \texttt{ProcessType}, as defined in previous subsection (\textbf{P10}). FML defines behavioral features called behavior. \texttt{ProcessType} defines the behavior \texttt{newProcess(String)}, taking the name of the process to enact as argument:

@@

The capture of \textbf{S3} requirement is performed while defining \inst{Coding} as an instance of concept \texttt{CodingTaskType} and defining a relation \texttt{languages} to \texttt{ProgrammingLanguage} with 1..* cardinality. 
\noteFabien{* dans la figure} The \texttt{newTask(String)} behavior overrides the generic implementation by instantiating a \texttt{CodingTask} concept, specializing \texttt{Task}, as shown in following excerpt of FML code:

>>>>

\texttt{Process} represents an enacted \texttt{ProcessType}, as defined in previous subsection (\textbf{P10}). \FML defines behavioral features called behavior. \texttt{ProcessType} defines the behavior \texttt{newProcess(String)}, taking the name of the process to enact as argument:

@@

The capture of \textbf{S3} requirement is performed while defining \inst{Coding} as an instance of concept \texttt{CodingTaskType} and defining a relation \texttt{languages} to \texttt{ProgrammingLanguage} with 1..* cardinality. 
\noteFabien{* dans la figure} The \texttt{newTask(String)} behavior overrides the generic implementation by instantiating a \texttt{CodingTask} concept, specializing \texttt{Task}, as shown in following excerpt of \FML code:
